DATA 621 Homework #1

### 2019-09-24 hw1/doc/HW1.Rmd
Updated HW1.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
```

@@

```{r}
# Change 0's to NA so they too can be imputed
training <- training %>%
  mutate(TEAM_BATTING_SO = ifelse(TEAM_BATTING_SO == 0, NA, TEAM_BATTING_SO))
```

@@

```{r}
#cleaned$TEAM_BASERUN_SB <- temp$TEAM_BASERUN_SB

@@

```{r}
#cleaned$TEAM_BASERUN_CS <- temp$TEAM_BASERUN_CS
```

@@

```{r}
#cleaned$TEAM_PITCHING_SO <- temp$TEAM_PITCHING_SO
```

@@

```{r}
#cleaned[which(cleaned$TEAM_PITCHING_SO > 5346),"TEAM_PITCHING_SO"] <- NA
```

```{r}
training %>% 
  ggplot(aes(TEAM_PITCHING_SO)) + 
  geom_histogram(bins = 50) +
  geom_vline(aes(xintercept = mean(TEAM_PITCHING_SO, na.rm = T)), col = "red", lty = 2) +
  geom_vline(aes(xintercept = median(TEAM_PITCHING_SO, na.rm = T)), col = "green", lty = 2) +
  labs(x = element_blank(),
       y = "Count",
       title = "Distribution of Strikeouts Pitched",
       subtitle = "After Removing Invalid Data and Imputation",
       caption = "* Red line is the mean value and green is the median")
```

@@

```{r}
#cleaned$TEAM_FIELDING_DP <- temp$TEAM_FIELDING_DP
```

```{r}
#training  <- training %>%
#  na.omit()
  #select(-TEAM_BATTING_HBP)
# set.seed(1)
# fix_missing_vals <- training %>%
#   na.omit() %>%
#   preProcess(., "knnImpute")

# training_mean <- mean(training$TARGET_WINS)
# 
# training <- predict(fix_missing_vals, training)
# 
# training$TEAM_FIP <- (training$TEAM_PITCHING_HR * 13) + (3 * training$TEAM_PITCHING_BB) - (2 * training$TEAM_PITCHING_SO)
# 
# pp <- preProcess(training, method = c("BoxCox", "center", "scale"))
# training <- predict(pp, training)
```

```{r eval=FALSE, echo=FALSE}
library(rpart)
library(rpart.plot)
m1 <- rpart(TARGET_WINS ~ ., data = training, method = "anova")
rpart.plot(m1)
plotcp(m1)
```

```{r eval=FALSE, echo=FALSE}
# Specify 10-fold cross validation
ctrl <- trainControl(method = "cv",  number = 10)

# CV bagged model
bagged_cv <- training %>%
  na.omit() %>%
  train(
    TARGET_WINS ~ ., 
    data = .,
    method = "treebag",
    trControl = ctrl,
    importance = TRUE
  )

# assess results
bagged_cv

plot(varImp(bagged_cv))

imp <- varImp(bagged_cv)$importance %>% 
  data.frame() %>%
  rownames_to_column()
```

@@

ggplot(moneyball_test, aes(error))+
  geom_histogram(bins = 50)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(DMwR)
```

@@

```{r}
# Change 0's to NA so they too can be imputed
training <- training %>%
  mutate(TEAM_BATTING_SO = ifelse(TEAM_BATTING_SO == 0, NA, TEAM_BATTING_SO))

knn <- training %>% knnImputation()
impute_me <- is.na(training$TEAM_BATTING_SO)
training[impute_me,"TEAM_BATTING_SO"] <- knn[impute_me,"TEAM_BATTING_SO"] 
```

@@

```{r}
impute_me <- is.na(training$TEAM_BASERUN_SB)
training[impute_me,"TEAM_BASERUN_SB"] <- knn[impute_me,"TEAM_BASERUN_SB"]

@@

```{r}
impute_me <- is.na(training$TEAM_BASERUN_CS)
training[impute_me,"TEAM_BASERUN_CS"] <- knn[impute_me,"TEAM_BASERUN_CS"] 
```

@@

```{r}
impute_me <- is.na(training$TEAM_PITCHING_SO)
training[impute_me,"TEAM_PITCHING_SO"] <- knn[impute_me,"TEAM_PITCHING_SO"] 
```

@@

```{r}
training[which(training$TEAM_PITCHING_SO > 5346),"TEAM_PITCHING_SO"] <- NA

training %>% 
  ggplot(aes(TEAM_PITCHING_SO)) + 
  geom_histogram(bins = 50) +
  geom_vline(aes(xintercept = mean(TEAM_PITCHING_SO, na.rm = T)), col = "red", lty = 2) +
  geom_vline(aes(xintercept = median(TEAM_PITCHING_SO, na.rm = T)), col = "green", lty = 2) +
  labs(x = element_blank(),
       y = "Count",
       title = "Distribution of Strikeouts Pitched",
       subtitle = "After Removing Invalid Data and Imputation",
       caption = "* Red line is the mean value and green is the median")
```

@@

```{r}
impute_me <- is.na(training$TEAM_FIELDING_DP)
training[impute_me,"TEAM_FIELDING_DP"] <- knn[impute_me,"TEAM_FIELDING_DP"] 
```

@@

ggplot(moneyball_test, aes(error)) +
  geom_histogram(bins = 50)
